### 2018-05-08 Final Paper/paper.tex
Added more stuff to the paper.

\section{Acknowledgments}

\section{References}

>>>>

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank Stephanie Taylor for all of her amazing help guiding us through this project. We would also like to thank Michelle Farkas, from the Department of Chemistry at University of Massachusetts Amherst for the data.

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}
\bibitem{FourFit}
Zielinski T, Moore AM, Troup E, Halliday KJ, Millar AJ (2014). \emph{Strengths and Limitations of Period Estimation Methods for Circadian Data}. PLoS ONE 9(5):e96462. doi:10.1371/journal.pone.0096462

@Misc{,
  author =    {Eric Jones and Travis Oliphant and Pearu Peterson and others},
  title =     {{SciPy}: Open source scientific tools for {Python}},
  year =      {2001--},
  url = "http://www.scipy.org/",
  note = {[Online; accessed <today>]}
}

@Article{Hunter:2007,
  Author    = {Hunter, J. D.},
  Title     = {Matplotlib: A 2D graphics environment},
  Journal   = {Computing In Science \& Engineering},
  Volume    = {9},
  Number    = {3},
  Pages     = {90--95},
  abstract  = {Matplotlib is a 2D graphics package used for Python
  for application development, interactive scripting, and
  publication-quality image generation across user
  interfaces and operating systems.},
  publisher = {IEEE COMPUTER SOC},
  doi       = {10.1109/MCSE.2007.55},
  year      = 2007
}

@misc(MatlabOTB,
  key = {MATLAB Optimization Toolbox},
  title = {MATLAB Optimization Toolbox},
  year = {2017}
  note = {The MathWorks, Natick, MA, USA}
}

\end{thebibliography}
